The Calculus of Linear Constructions

### 2021-10-16 writing/draft3.tex
draft

  \subsubsection{Promotion and Dereliction}
  In most presentations of linear logic, non-linear objects are created by packing linear objects under non-linear contexts into the ! exponential through the \textit{promotion} rule. Conversely, the \textit{dereliction} rule unpacks non-linear objects so they can be used in place of linear ones. Linear type theories \cite{abramsky1993,dill,vakar14} utilizing exponential for non-linearity will contain ! types and rules that are equivalent to \textit{promotion} and \textit{dereliction}.

>>>>

  \subsubsection{Promotion and Dereliction}
  In most presentations of linear logic, non-linear objects are created by packing linear objects into the ! exponential using the \textit{promotion} rule. Conversely, the \textit{dereliction} rule unpacks non-linear objects so they can be used in place of linear ones. Linear type theories \cite{abramsky1993,dill,vakar14} utilizing exponential for non-linearity will contain ! types and rules that are equivalent to \textit{promotion} and \textit{dereliction}.
